X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt}

### 2013-09-09 hedpc_natphys.tex
Changed figure 2 to SEM image. Added acknowledgements.
    - SEM image (Au_grating)
    - Acknowledge Peter, Istvan, CCMX
    - copied library.bib here (was simlink to cDPC project folder)

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Figure~\ref{Fig:grating_mask}. Each grating resides on a
silicon chip and has its specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy \cite{David2002}. Using
gold as the phase shifting material, this requires a structure length of
$h_1 = \SI{19.8}{\micro \metre}$. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter \cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$, this grating has an aspect ratio of $2h/p \approx
570$ and thus sufficiently attenuates X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. Beam splitter- and analyzer grating are
separated at the first fractional Talbot order \cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources \cite{Pfeiffer2006}. It is also made of gold structures
with a structure length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure} [ht]
    \includegraphics[width=.5\textwidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach. (a) Top part of the 4 inch wafer,
        showing five grating chips; one source grating, two beam splitter
        gratings and two analyzer gratings (from top to bottom). The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. (b) Zoom into the grating structures,
        contain interrupting bridges used for stabilizing the grating
        structures in the lithographic process \cite{Kenntner2010}.}
        \label{Fig:grating_mask}
\end{figure}

@@

\section*{Acknowledgements} We thank Gordan Mikuljan from Paul Scherrer
Institute, Switzerland, for his work on the mechanical design, Joachim
Schulz and Marco Walter from Microworks GmbH, Germany, for the competent
support on grating design issues, Christian Kottler and Vincent Revol from
Centre Suisse d'Electronique et de Microtechnique (CSEM), Switzerland for
the fruitful discussions on the design of the system.
Part of this work has been supported by the ERC Grant ERC-2012-StG 310005-PhaseX.

>>>>

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Figure~\ref{Fig:grating_mask}. Each grating resides on a
silicon chip and has its specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy \cite{David2002}. Using
gold as the phase shifting material, this requires a structure length of
$h_1 = \SI{19.8}{\micro \metre}$. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter \cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$, this grating has an aspect ratio of $2h/p \approx
570$ and thus sufficiently attenuates X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. Beam splitter- and analyzer grating are
separated at the first fractional Talbot order \cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources \cite{Pfeiffer2006}. It is also made of gold structures
with a structure length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure} [ht]
    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach and scanning electron microscope
        image of the grating. The top part of the 4 inch wafer shows
        five grating chips. The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. 
        The interrupting bridges used for stabilizing the grating
        in the lithographic process can be seen with the SEM\cite{Kenntner2010}.}
        \label{Fig:grating_mask}
\end{figure}

@@

\section*{Acknowledgements}
We thank Gordan Mikuljan, Peter Modregger and István Mohácsi from the Paul
Scherrer Institute (PSI), Switzerland, for the
work on the mechanical design, the scientific advice, and the SEM images
respectively, Joachim Schulz and Marco Walter from
Microworks GmbH, Germany, for the competent support on grating design
issues, Christian Kottler and Vincent Revol from Centre Suisse
d'Electronique et de Microtechnique (CSEM), Switzerland for the fruitful
discussions on the design of the system. This work has been partially
supported by the Competence Centre for Materials Science and Technology
(CCMX) of the ETH-Board, Project Nr. 61 and by the ERC Grant ERC-2012-StG 310005-PhaseX.
